---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# promis

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/promis)](https://CRAN.R-project.org/package=promis)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Codecov test coverage](https://codecov.io/gh/nt-williams/promis/branch/master/graph/badge.svg)](https://codecov.io/gh/nt-williams/promis?branch=master)
[![Travis build status](https://travis-ci.com/nt-williams/promis.svg?branch=master)](https://travis-ci.com/nt-williams/promis)
<!-- badges: end -->

> Implementation of an S3 vector class for the [PROMIS](http://www.healthmeasures.net/explore-measurement-systems/promis) health measure

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("nt-williams/promis")
```

## Usage

```{r}
df <- tibble::tibble(x = c(45, 20, 80, 60, 72, 33))
df
```

Numeric vectors can be converted to a `promis` vector with the `promis()` function.

```{r}
library(promis)

df <- dplyr::mutate(df, x = promis(x, domain = "Physical function"))
df

df$x

is_promis(df$x)
```

`promis` vectors encode information about score cutoffs for the specific domain. This allows converting numeric PROMIS scores to their categories by just calling `as.character()`.

```{r}
dplyr::mutate(df, cutoff = as.character(x))
```



